Personalization and probabilities: the expression of propensities in online grocery shopping

### 2017-07-31 log.rmd
lu print

## Fri 28 Jul 2017 12:18:30 BST
- adding the hadoop stuff as a footnote to para on local mods.  
- moved the personalization stuff into the intro
- starting to rewrite the abstract; finished a version of it. 
- DONE: go through and fix subheadings
- TODO: go through TODOs
- TODO: print

>>>>

## Fri 28 Jul 2017 12:18:30 BST
- adding the hadoop stuff as a footnote to para on local mods.  
- moved the personalization stuff into the intro
- starting to rewrite the abstract; finished a version of it. 
- DONE: go through and fix subheadings
- TODO: go through TODOs
- DONE: print

## Mon 31 Jul 2017 11:47:42 BST
- printing as docx. There are around 35 pages on manuscript. Plan for revision: 7 pages/day for one week; (7 hours)  go through referee reports again alongside the manuscript to put them in (2 hours); redo diagrams and references (3 hours), submission (1 hour). Total of about 12 hours. Might be to do about 6-7 hours this week.
